Simulation

### 2024-06-24 Simulation1.Rmd
Montag Abend

```{r}
trees <- read_excel("~/work/Sim_article2024/artificial_forest_round.xls")
```

@@

```{r}
# First visualisation
plot(x = trees$x, y = trees$y, main = "Forest")
```

```{r}
# True values
cat("Il y a au total", length(trees$x), "arbres et un volume total de", sum(trees$v), "\n", "Soit un volume moyen de", mean(trees$v), "\n", "Le diamètre moyen à hauteur de poitrine est de", mean(trees$d130))
```

```{r}
plot(x = trees$x, y = trees$y, main = "Forest", panel.first=grid())
```

@@

We need to create another variable to indicate in which cell is each tree

@@

```{r}
trees$cell <- rep(0, 30942) # Initialisation de la variable
```

@@

## 2nd step (2 for loops)
All the lines, still one number

```{r}
list_stable <- list
```

@@

```{r}
# When only focusing on 1 10th of the population
plot(x = trees[(trees$cell == 5) & (trees$x >= 300) & (trees$x < 310),]$x, y = trees[(trees$cell == 5) & (trees$x >= 300) & (trees$x < 310),]$y, main = "Echantillonnage", panel.first=grid())
```

@@

```{r}
# Function to check if a point is inside the circle
is_point_in_circle <- function(x, y, h, k, R) {
  # Calculate the squared distance between the point and the center of the circle
  squared_distance <- (x - h)^2 + (y - k)^2
  # Check if the squared distance is less than or equal to the squared radius
  return(squared_distance <= R^2)
}

trees$Is_in_circle <- is_point_in_circle(a, b, trees$x, trees$y, 5)
```

@@

```{r}
## A modifier 
# (k + (l-1)*60 -1)%%600 + 1

@@

@@

@@

```{r}
plot(x = random_points[(random_points$x < 210),]$x, y = random_points[(random_points$x < 210),]$y, main = "Random points", panel.first=grid(), xlim = c(200, 210), ylim = c(200, 220))
# Semble régulier si nb = 2
# Probleme : 2 fois trop de points tirés 
```

```{r}
plot(x = random_points[(random_points$x < 210),]$x, y = random_points[(random_points$x < 210),]$y, main = "Random points", panel.first=grid(), xlim = c(202, 205), ylim = c(200, 205))
# Il arrive qu'il y ait 2 points dans la même cellule...
```

```{r}
plot(x = random_points[(random_points$x < 210),]$x, y = random_points[(random_points$x < 210),]$y, main = "Random points", panel.first=grid(), xlim = c(200, 210), ylim = c(200, 220))
# Semble régulier si nb = 2
# Probleme : 10 fois trop de points
```

@@

>>>>

```{r}
# Importing the database with the artificial forest
trees <- read_excel("~/work/Sim_article2024/artificial_forest_round.xls")
```

@@

```{r}
# First visualization
plot(x = trees$x, y = trees$y, main = "Forest")
# All trees have coordinates (abscissa and ordinate) between 200 and 800
```

```{r}
# True values
cat("Il y a au total", length(trees$x), "arbres et un volume total de", sum(trees$v), "m^3 \n", "Soit un volume moyen de", mean(trees$v), "m^3 \n", "Le diamètre moyen à hauteur de poitrine est de", mean(trees$d130), "cm")
```

@@

We may create another variable to indicate in which cell is each tree.

@@

```{r}
trees$cell <- rep(0, 30942) # Initialization of the variable
```

3 steps to assign a type of cell (i.e. a number between 1 and 10) to every trees

@@

## 2nd step (2 for loops)
All the lines, still one number
```{r}
list_stable <- list
```

@@

```{r}
# When only focusing on 1 10th of the population but with more precision
plot(x = trees[(trees$cell == 5) & (trees$x >= 300) & (trees$x < 310),]$x, y = trees[(trees$cell == 5) & (trees$x >= 300) & (trees$x < 310),]$y, main = "Echantillonnage", panel.first=grid())
```

@@

```{r}
# Function to check if a point is inside the circle
is_point_in_circle <- function(x, y, h, k, R) {
  # Calculate the squared distance between the point and the center of the circle
  squared_distance <- (x - h)^2 + (y - k)^2
  # Check if the squared distance is less than or equal to the squared radius
  return(squared_distance <= R^2)
}
```

```{r}
trees$Is_in_circle <- is_point_in_circle(a, b, trees$x, trees$y, 5)
```

@@

```{r}
# It works a priori
# l: toutes les lignes ; k: les cellules sur une ligne ; a: abscisse ; b: ordonnée

@@

# 36 000 points are randomly selected if nb = 5
# Which is what we want!

@@

```{r}
rm(a,b,k,l) # Useless outside loops
```

@@

```{r}
# plot(x = random_points[(random_points$x < 210),]$x, y = random_points[(random_points$x < 210),]$y, main = "Random points", panel.first=grid(), xlim = c(200, 210), ylim = c(200, 220))
# Semble régulier si nb = 2
# Probleme : 2 fois trop de points tirés 
```

```{r}
# plot(x = random_points[(random_points$x < 210),]$x, y = random_points[(random_points$x < 210),]$y, main = "Random points", panel.first=grid(), xlim = c(202, 205), ylim = c(200, 205))
# Il arrive qu'il y ait 2 points dans la même cellule...
```

```{r}
plot(x = random_points[(random_points$x < 210),]$x, y = random_points[(random_points$x < 210),]$y, main = "Random points", panel.first=grid(), xlim = c(200, 210), ylim = c(200, 220))
# Semble régulier si nb = 2
```

@@

# Circles around random points

```{r}
# Adding columns to the dataframe
# Number of trees inside each circle around each random point ; Total of diameter ; Total volume
for (point in 1:36000) {
  trees$Is_in_circle <- is_point_in_circle(a, b, trees$x, trees$y, 5)
  # x, y, h, k, R
  total_trees <- nrow(trees[trees$Is_in_circle == TRUE,])
  total_d130 <- sum(trees[trees$Is_in_circle == TRUE,]$d130)
}
random_points
```

```{r}
# Creating the local variable
# Formule pages 10-11 de Chauvet et alii (2024)
M_k <- function(x, y, h, k, R) {

}
```
